\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal

### 2014-06-16 article.tex
fix a typo

% Solution
In this paper, we describe a simple and a theoretically grounded approach
based on partial correlation\footnote{Source code is available at
\url{https://github.com/asutera/kaggle-connectomics}.} to infer the neural
network, which is the winning method of the Connectomics challenge
\footnote{\url{http://connectomics.chalearn.org}}.

@@

% However, the image fluorescence calcium signal is also very noisy. Thus,
% A low-pass filter (Equation \ref{eq:low-pass}) is first applied followed by a
% high-pass filter (Equation \ref{eq:high-pass}), the discrete derivative of
% the signal,
% \begin{align}
% X^\prime_{t,i} &= \sum_{l=-3}^2 c_l^k X_{t+l,i} \forall i, \label{eq:low-pass}\\
% X^{\prime\prime}_{t,i} &= X^{\prime}_{t,i} - X^{\prime}_{t-1,i} \forall i, \label{eq:high-pass}
% \end{align}
% where the $c_l^k$ coefficients were taken in one of the four
% following tuples
% $\left(c_l^1\right)_{l=-3}^2=(0, 0, 1, 1, 1, 1)$,
% $\left(c_l^2\right)_{l=-3}^2=(0, 0, 1, 1, 1, 0)$,
% $\left(c_l^3\right)_{l=-3}^2=(1, 1, 1, 1, 0, 0)$ or
% $\left(c_l^4\right)_{l=-3}^2=(0.4, 0.8, 1, 1, 0, 0)$.

@@

% Metrics : ROC AUC and AUPRC
In supervised learning terms, the network inference task can be viewed as a
binary classification task where one has to correctly classify the presence
or the absence of edges of the graph. We assess the accuracy of the
network inference method using the area under the ROC curve (AUROC)
and the area under the precision-recall curve (AUPRC)
(\cite{schrynemackers2013protocols}). Since neurons are not self-connected
($(i, i) \not \in E, \forall i \in V$) and some inference methods could
give maximal scores to the diagonal of $\hat{A}$, e.g. Pearson
correlation, we set those elements to the minimum of $\hat{A}$ prior
assessment.

>>>>

% Solution

In this paper, we describe a simple and a theoretically grounded approach
based on partial correlation\footnote{Source code is available at
\url{https://github.com/asutera/kaggle-connectomics}.} to infer the neural
network, which is the winning method of the Connectomics challenge
\footnote{\url{http://connectomics.chalearn.org}}.

@@

@@

% Metrics : ROC AUC and AUPRC
In supervised learning terms, the network inference task can be viewed as a
binary classification task where one has to correctly classify the presence
or the absence of edges of the graph. Given the ground true adjacency matrix
$A$ and a connectivity score matrix $\hat{A}$, we assess the accuracy of the
network inference method using the area under the ROC curve (AUROC)
and the area under the precision-recall curve (AUPRC)
(\cite{schrynemackers2013protocols}). Since neurons are not self-connected
($(i, i) \not \in E, \forall i \in V$) and some inference methods could
give maximal scores to the diagonal of $\hat{A}$, e.g. Pearson
correlation, we set those elements to the minimum of $\hat{A}$ prior
assessment.
